---
title: "linear model from Web"
author: "Leah Riganyan"
date: "Spring Semester 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```
   
The plot shows the simulated expectations of arm strength in workers. Most of the population has an arm strength between 50 to 100.
   

### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```
   
The numerical results show us the relationship between SIMS and ARM are the same. The bigger the number we get, the larger they correlate. We can see that there is little correlation between the two.

### Inferential  (Build model.1)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation for the line in this scenario is SIMS=0.054563xARM-4.095160. Because of the positive coefficient, the line also moves in a positive direction, lower left to upper right.

#### Predict at target point
   
```{r}
tgtpoint=data.frame(ARM=88, GRIP=94)

predict(model.1,tgtpoint, interval= c("prediction"))
```
   
This table shows the predicted target plot is 0.7063836, bu at 95% we are going to have a value between -1.726209 3.138977.

#### scatterplot with model fit
   
```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size =  20)) + geom_smooth(method=lm)
```
   
The data above is showing us the line of best fit from the data collected from SIMS vs ARM. The line shows us which data point is closest to the expected result.
   

## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
basicGRIP <- ggplot(data,aes(y=SIMS,x=GRIP))
basicGRIP + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```



### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
  
The numerical result for SIMS vs GRIP is 0.6398458, compared to SIMS vs ARM which was 0.6860073. The value is bigger for SIMS vs ARM, meaning the correspondence is smaller between the data tables. SIMS vs ARM's model is more accurate than the SIMS vs GRIP model.

### Inferential  (Build model.2)
   
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
   
The inferential result for model 2 shows us the equation as SIMS = 0.045463x GRIP -4.809675 for the line of best fit. The positive coefficient makes the slope positive, so we'll see the line from the bottom left travel to the upper right.
   
#### predict model.2 at target point
   
```{r}
predict(model.2, tgtpoint, interval=c("prediction"))
```

The prediction model shows us the best fit value is -0.5361543, but that 95% the time the value will be between -3.107961, and 2.035652.

#### now add the model fit to our plot for model.2
```{r}
basicGRIP + geom_point() + ggtitle("SIMS vs GRIP") + theme(plot.title = element_text(hjust = 0.5, size = 20)) + geom_smooth(method=lm)
```
   
The scatter plot for SIMS v GRIP shows us the best line of fit, showing us the most accurate data points.
   

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)
   
```{r}
cor(SIMS~ARM+GRIP,data=data)
```
   
The numerical results here show us that there's a 0.7326545 correlation between SIMS vs ARM+GRIP. This tells us that the most accurate model would be this one, rather than individually looking at ARM/GRIP separately. 

### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```
   
The data gives us the equation of SIMS = 0.037311xARM + 0.024470xGRIP -5.433871 as the plane of best fit.
   
#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

